Market Simulator

### 2020-08-20 analysis/05_market_simulator.Rmd
added org name inputs and render gauges for orgs and personas

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))

@@

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("ai_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"))

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

selectInput("ai_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"))
```

```{r ai gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

@@

renderGauge({
  choice = df()
  persona = p_beta2 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

@@

renderGauge({
  choice = df()
  persona = p_beta3 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

@@

```{r gp org inputs}
selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

```{r gp gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

@@

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})
```

@@

```{r ox org inputs}
selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

```{r ox gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

@@

```{r rc org inputs}
selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

```{r rc gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)

@@

@@

# selectInput("p1_political_pref",
#          label = "Political views from liberal to conservative:",
#          choices = c("0", '1', '2', '3','4','5','6','7'))

@@

@@

@@

@@

>>>>

  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))

@@

textInput("ai_id",
          label = "Organization Name",
          value = "Organization 1",
          placeholder = "Enter Organiation Name",
          width = "200px")

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            width = "200px")

selectInput("ai_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            width = "200px")

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"),
            width = "200px")

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"),
            width = "200px")

selectInput("ai_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            width = "200px")

```{r ai gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

@@

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

@@

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

@@

```{r gp org inputs}

textInput("gp_id",
          label = "Organization Name",
          value = "Organization 2",
          placeholder = "Enter Organiation Name"
)

selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

```{r gp gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

@@

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

@@

```{r ox org inputs}

textInput("ox_id",
          label = "Organization Name",
          value = "Organization 3",
          placeholder = "Enter Organiation Name"
)

selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

```{r ox gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

@@

```{r rc org inputs}

textInput("rc_id",
          label = "Organization Name",
          value = "Organization 4",
          placeholder = "Enter Organiation Name"
)

selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

```{r rc gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

@@

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

@@

@@

```{r persona 1 gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

@@

```{r persona 2 gauge}
renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

@@

```{r persona 3 gauge}
renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

@@

<!-- This is for commented out code -->
